Using NSGA-II to compose model transformations alternatives

### 2014-10-29 SysCon_article/article_syscon.tex
modification of the section related work

%modeling solution for their application, platform, and mapping between application and platform, in an integrated and simultaneous way and at a very early design stage, before system synthesis and code generation have been performed.

%multi-objective optimization evolutionary algorithms which is known to be an important tool for design decision making support.

%The design of safety-critical systems becomes one of the most interesting challenges in modern systems engineering. It requires system architects to address a large number of non-functional properties related to performance, reliability, availability and temporal performance. Moreover, these non-functional properties often conflict with each other, for instance, improving system performance often needs more powerful hardware components, which increases the production cost and power consumption in the meantime.

%and model transformation strategies to identify a sufficient set of design alternatives. This approach will reduce development costs and improve the quality of the final system, because an automated and systematic search will identify more and better design alternatives.

%In this paper, we propose an approach which can analyse a given system architecture, propose design alternatives to it by using model transformations, and do architecture optimization by using some evolutionary algorithms to improve its non-functional properties in an automatic way.
\end{abstract}

%This paper proposes to use multi-objective optimization evolutionary algorithms and model transformation strategies to identify a sufficient set of design alternatives. This approach will reduce development costs and improve the quality of the final system, because an automated and systematic search will identify more and better design alternatives.

% no keywords

@@

The reminder of this paper is organized as follows. Section~\ref{Problem} is dedicated to the problem statement. Section~\ref{Approach} gives an overview  of our approach. While Section~\ref{Adapting} details our approach. Section~\ref{Related} presents the related work.
%The remainder of this paper is organized as follows. Section~\ref{Problem} is dedicated to the problem statement. Section~\ref{Approach} gives an overview  of our approach. While Section~\ref{Adapting} details our approach. Section~\ref{Related} presents the related work. Finally, conclusions and perspectives are given in Section~\ref{Conclu}.

@@

%These design patterns are implemented as model transformations. It  which allows us to applied them to various sets of NFP

%improving a set NFP, and solving the conflict between these NFP.  Model transformations are usually defined to be generic such as design patterns which allows us to applied them to various sets of NFP.

%A set of model transformations that implement refinements or improvements of the source model, each of them focusing on increasing the satisfaction of a given goal (reducing power consumption, increasing availability, etc.). These model transformations can be seen as design patterns, each of them implementing a well-known solution to a given quality objective.

%A possible solution to this issue is to formalize design alternatives so they can be reusable in different products or projects (i.e. by using model transformation techniques). After the formalization step, explore the design space to identify the set of optimal model transformation alternatives : solutions that fulfils most NFP.

@@

\subsection{System architecture modelisation}
%For software architecture modeling step, as a natural extension of previous work RAMSES and  we choose to use AADL (Architecture Analysis & Design Language) as the underlying architecture description language.

Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language. AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of quality analysis (e.g. safety); and (ii) design architectures for complex embedded systems. It offers a standardized semantics, mostly expressed using natural language and the components are composed hierarchically according to standardized composition rules. AADL also allows the designers to expand model by defining new property sets in their own specific way. The other reason of choosing AADL is to integrate our work in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems. \url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.

@@

%These languages define rules which define the mapping from source elements (elements of the software architecture) to target element (architecture alternative).

@@

%\subsection{Adapting NSGA-II To explore the design space}
%The second step of our approach consists in (i) the exploration of the design space (composed of the set of genomes described above); and (ii) selection of the optimal genomes. This step is realised by adapting the concepts of the NSGA-II algorithm to our design problem. To do so, we use the same algorithm as described previously. Except that each genome is represented by a set of TRA.

@@

%In the genetic algorithm used in the evolutionary design system above the genotypes consist of 1's and 0's, applying the mutation operator to a genotype of this kind switches a randomly selected 1 to a 0 or vice versa. 
%Indicating the core in the tile TRA as cs and ct as the core with which cs communicates most frequently, cs is remapped on a tile adjacent to Ts so as to reduce the distance between cs and ct . thus obtaining the mutated chromosome C0.

@@

%\subsection{\textbf{Use case}}
%Figure~\ref{nsgaDesign} gives an overview of the application of

%\begin{figure}[!t]
%\centering
%\includegraphics[width=3.49in]{nsgaDesign.pdf}
%\caption{Overview of the adaptation of NSGA-II}
%\label{nsgaDesign}
%\end{figure}

@@

\subsection{model transformations techniques}
Recently, several works

\subsection{multi-objective metaheuristic optimization}
Aleti et al.\cite{Gr5069138} have developed the ArchOpteryx framework. ArchOpteryx assists the system architects during the design to create architectures that meet non-functional properties by using multi-objective optimization strategies. Unlike this method, design alternatives are implemented as model transformations driven by NFP. Using model transformations help the design architects to (i) automating the system production; (ii) reusing architecture alternatives in other projects (or products) and (iii) solving the competition issue between NFP. Compared to DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, in our method model transformations are not decomposed into subplans, each transformation is performed atomically.

Koziolek et al.\cite{Koziolek:2011:PAA:2000259.2000267} have developed the Peropteryx framework for improvement of system architecture models using a metaheuristic search guided by architectural tactics.

@@

%Older works and experiments have shown that evolutionary algorithms and multiobjective optimization strategies can be used to identify Pareto-optimal or near Pareto-optimal architecture designs, which can be used as an input for architecture trade-off analysis techniques.

%The main benefit of this approach is the ability to handle the large search spaces of quality optimization problems and to automate the identification of good architecture design alternatives. This will reduce development costs and improve the quality of the final system. Addition- ally this approach enables the ranking of design decisions (architectural refactorings) with respect to conflicting quality requirements.

@@

@@

@@

>>>>

\end{abstract}

@@

The reminder of this paper is organized as follows. Section~\ref{Problem} is dedicated to the problem statement. Section~\ref{Approach} gives an overview  of our approach. While Section~\ref{Adapting} details our approach. Section~\ref{Related} presents the related work.

@@

@@

\subsection{System architecture modelisation}
Since our application domain is embedded systems, we have chosen AADL (Architecture Analysis \& Design Language) as the underlying architecture description language. AADL has been designed on the foundation of the architecture description language MetaH and its goals are (i) specification of quality analysis (e.g. safety); and (ii) design architectures for complex embedded systems. It offers a standardized semantics, mostly expressed using natural language and the components are composed hierarchically according to standardized composition rules. AADL also allows the designers to expand model by defining new property sets in their own specific way. The other reason of choosing AADL is to integrate our work in an existing framework RAMSES\footnote{Refinement of AADL Models for the Synthesis of Embdded Systems. \url{http://penelope.enst.fr/aadl/wiki/Projects}} which apply selection of design alternatives.

@@

@@

@@

@@

@@

\subsection{model transformations techniques}
Recently, some works have focused on the definition of model transformation alternatives. The first works introduced the superimposition mechanism\cite{Navarro:2011:UMT:2041790.2041840} to implement transformations alternatives. Another work\cite{Kavimandan:2011:MQS:2000259.2000264} proposed to implement transformations alternatives by using rule-based transformation languages. These works has been continued in\cite{Drago:2011} in order to deal with architecture quality problems.

Our contribution is based on this work since it enable the factorization and composition of model transformations. However, this approach doesn't propose any algorithm to select the non-dominated (or pareto) model transformations alternatives which fulfil at best a set of competing non-functional properties.

\subsection{multi-objective metaheuristic optimization}
Aleti et al.\cite{Gr5069138} have developed the ArchOpteryx framework. ArchOpteryx assists the system architects during the design phase to create architectures that meet non-functional properties by using multi-objective optimization strategies.

Koziolek et al.\cite{Koziolek:2011:PAA:2000259.2000267} also developed their own framework Peropteryx for improvement of system architecture models using a metaheuristic search guided by architectural tactics.

Unlike these two frameworks, in our approach design alternatives are implemented as model transformations driven by NFP. The use of model transformations help the design architects to (i) automating the system production; (ii) reusing architecture alternatives in other projects (or products) and (iii) solving the competition issue between NFP.

Compared to DesignBots\cite{Diaz-Pace:2007:UPT:1784860.1784865}, in our method model transformations are not decomposed into subplans, each transformation is performed atomically.

@@

@@

\bibitem{Drago:2011}
M.~Drago, C.~Ghezzi, and R.~Mirandola, ``Towards quality driven exploration of
  model transformation spaces,'' in \emph{Model Driven Engineering Languages
  and Systems}, ser. Lecture Notes in Computer Science, J.~Whittle, T.~Clark,
  and T.~Kühne, Eds., vol. 6981.\hskip 1em plus 0.5em minus 0.4em\relax
  Springer Berlin Heidelberg, 2011, pp. 2--16. [Online]. Available:
  \url{http://dx.doi.org/10.1007/978-3-642-24485-8_2}

@@

\bibitem{Kavimandan:2011:MQS:2000259.2000264}
A.~Kavimandan, A.~Gokhale, G.~Karsai, and J.~Gray, ``Managing the quality of
  software product line architectures through reusable model transformations,''
  in \emph{Proceedings of the Joint ACM SIGSOFT Conference -- QoSA and ACM
  SIGSOFT Symposium -- ISARCS on Quality of Software Architectures -- QoSA and
  Architecting Critical Systems -- ISARCS}, ser. QoSA-ISARCS '11.\hskip 1em
  plus 0.5em minus 0.4em\relax New York, NY, USA: ACM, 2011, pp. 13--22.
  [Online]. Available: \url{http://doi.acm.org/10.1145/2000259.2000264}

@@

\bibitem{Navarro:2011:UMT:2041790.2041840}
E.~Navarro, C.~E. Cuesta, D.~E. Perry, and C.~Roda, ``Using model
  transformation techniques for the superimposition of architectural styles,''
  in \emph{Proceedings of the 5th European Conference on Software
  Architecture}, ser. ECSA'11.\hskip 1em plus 0.5em minus 0.4em\relax Berlin,
  Heidelberg: Springer-Verlag, 2011, pp. 379--387. [Online]. Available:
  \url{http://dl.acm.org/citation.cfm?id=2041790.2041840}
